Neonatal models

### 2021-12-14 getdata2.Rmd
modifications ...

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
library(eha)
library(skum)
options(show.signif.stars = FALSE)
g <- function(x) (log(1 + 365 * x))^3
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
library(eha)
library(skum)
options(show.signif.stars = FALSE)
g <- function(x) (log(1 + x))^3 # x is time in days! #### Note ###
```

### 2021-12-14 neo2.Rmd
modifications ...

How to analyse table data with the same statistical models, for instance *Cox regression*,
as you are used to with individual data, is shown here. It helps if you have the 
**R** package *eha* [@eha; @ehar2] for easy conversion of individual data to tabular
suitable for survival analysis.

@@

```{r clean}
neo <- neo[neo$parity > 0, ] # Remove missing = -1
neo$parity <- cut(neo$parity, c(0, 1.5, 3.5, 18.5), labels = c("1", "2-3", "4+"))
neo$socStatus[is.na(neo$socStatus)] <- "low"
x <- head(neo) ## OK
tbl(x, caption = "Raw individual data.")
```

@@

```{r tabulate}
tneo <- toTpch(Surv(enter, exit, event) ~  
                   sex + socStatus + illeg + parity, 
               data = neo, cuts = 0:28)
DIMT <- dim(tneo)
X <- head(tneo)
##summary(tneo)
tbl(X, caption = "Same data, tabular form.")
saveRDS(tneo, file = "t_data/tneo.rds")
```

@@

The age interval is cut into 28 pieces, "0-1", "1-2", etc., so the underlying statistical survival model is that of a *piecevise constant hazards*.

>>>>

How to analyse table data with the same statistical models, for instance *Cox regression*,
as you are used to with individual data, is shown here. It helps if you have the 
**R** package *eha* [@eha; @ehar2] for easy conversion of individual data to tabular data
suitable for survival analysis.

@@

```{r clean}
neo <- neo[neo$parity > 0, ] # Remove missing = -1
neo$parity <- cut(neo$parity, c(0, 1.5, 3.5, 18.5), labels = c("1", "2-3", "4+"))
neo$socStatus[is.na(neo$socStatus)] <- "low"
x <- head(neo) ## OK
tbl(x, caption = "Raw individual data, age in days. First few rows.")
```

@@

```{r tabulate}
tneo <- toTpch(Surv(enter, exit, event) ~  
                   sex + socStatus + illeg + parity, 
               data = neo, cuts = 0:28)
DIMT <- dim(tneo)
X <- head(tneo)
##summary(tneo)
tbl(X, caption = "Same data, tabular form, age in days. First few rows.")
saveRDS(tneo, file = "t_data/tneo.rds")
```

@@

The age interval $(0, 28]$ is cut into 28 pieces, (0-1], (1-2], etc., so the underlying statistical survival model is that of a *piecevise constant hazards*.
